Who does big team science?

### 2022-06-06 03.data_analysis.Rmd
updating manuscript pre-reg

# map of degree representation ----
o_ed_summary <- o_ed %>% 
  group_by(ORCID) %>% 
  arrange(desc(education_summary_start_date_year_value)) %>% 
  ungroup() %>% 
  filter(!duplicated(ORCID)) %>% 
  select(ORCID, education_summary_organization_address_country)

# summarize the same samples
o_ed_country <- o_ed_summary %>% 
      group_by(education_summary_organization_address_country) %>% 
      summarize(n = n()) %>% 
      filter(!is.na(education_summary_organization_address_country))

@@

gpr_effects_ed <- data.frame(
  TITLE = titles, 
  year = years, 
  v = NA, 
  low_v = NA, 
  high_v = NA
)

gpr_effects_job <- data.frame(
  TITLE = titles, 
  year = years, 
  v = NA, 
  low_v = NA, 
  high_v = NA
)

# for (i in 1:length(first_probs_ed)){
#   first_ed <- first_probs_ed[[i]]
#   first_job <- first_probs_job[[i]]
#   last_ed <- last_probs_ed[[i]]
#   last_job <- last_probs_job[[i]]
#   
#   ed <- first_ed %>% full_join(last_ed, by = c("Var1" = "Var1")) %>% filter(Var1 != "<NA>")
#   ed$Freq.x[is.na(ed$Freq.x)] <- 0
#   ed$Freq.y[is.na(ed$Freq.y)] <- 0
#   ed_chi <- chisq.test(ed[ , c("Freq.x", "Freq.y")])
#   
#   ed_mote <- v.chi.sq(x2 = ed_chi$statistic, 
#                       n = sum(ed_chi$observed), 
#                       r = nrow(ed_chi$observed),
#                       c = ncol(ed_chi$observed))
#   
#   gpr_effects_ed$v[i] <- ed_mote$v
#   gpr_effects_ed$low_v[i] <- ed_mote$vlow
#   gpr_effects_ed$high_v[i] <- ed_mote$vhigh
#   
#   job <- first_job %>% full_join(last_job, by = c("Var1" = "Var1")) %>% filter(Var1 != "<NA>")
#   job$Freq.x[is.na(job$Freq.x)] <- 0
#   job$Freq.y[is.na(job$Freq.y)] <- 0
#   job_chi <- chisq.test(job[ , c("Freq.x", "Freq.y")])
#   
#   job_mote <- v.chi.sq(x2 = job_chi$statistic, 
#                       n = sum(job_chi$observed), 
#                       r = nrow(job_chi$observed),
#                       c = ncol(job_chi$observed))
#   
#   gpr_effects_job$v[i] <- job_mote$v
#   gpr_effects_job$low_v[i] <- job_mote$vlow
#   gpr_effects_job$high_v[i] <- job_mote$vhigh
# 
# }
```

>>>>

# map of degree representation ----
o_ed_summary_map <- o_ed %>% 
  group_by(ORCID) %>% 
  arrange(desc(education_summary_start_date_year_value)) %>% 
  ungroup() %>% 
  filter(!duplicated(ORCID)) %>% 
  select(ORCID, education_summary_organization_address_country)

# summarize the same samples
o_ed_country <- o_ed_summary_map %>% 
      group_by(education_summary_organization_address_country) %>% 
      summarize(n = n()) %>% 
      filter(!is.na(education_summary_organization_address_country))

@@

gpr_effects_ed <- bind_rows(first_probs_ed, .id = "source") %>% 
  full_join(
    bind_rows(last_probs_ed, .id = "source"), 
    by = c("source" = "source", "Var1" = "Var1")
  ) %>% 
  full_join(
    data.frame(TITLE = titles, year = years, 
               source = as.character(1:length(titles))),
    by = c("source" = "source")
  )
colnames(gpr_effects_ed) <- c("source", "unregion", "freq_first", 
                              "freq_last", "TITLE", "year")

gpr_effects_job <- bind_rows(first_probs_job, .id = "source") %>% 
  full_join(
    bind_rows(last_probs_job, .id = "source"), 
    by = c("source" = "source", "Var1" = "Var1")
  ) %>% 
  full_join(
    data.frame(TITLE = titles, year = years, 
               source = as.character(1:length(titles))),
    by = c("source" = "source")
  )
colnames(gpr_effects_job) <- c("source", "unregion", "freq_first", 
                               "freq_last","TITLE", "year")

# flatten down by year breakdown 
gpr_effects_ed$group <- NA
gpr_effects_ed$year <- as.numeric(gpr_effects_ed$year)
gpr_effects_ed$group[gpr_effects_ed$year < 2020] <- "Pre-2020"
gpr_effects_ed$group[gpr_effects_ed$year == 2020] <- "2020"
gpr_effects_ed$group[gpr_effects_ed$year > 2020] <- "Post-2020"

gpr_effects_ed_summary <- gpr_effects_ed %>% 
  select(group, unregion, freq_first, freq_last) %>% 
  group_by(group, unregion) %>% 
  summarize(total_first = sum(freq_first, na.rm = T),
            total_last = sum(freq_last, na.rm = T)) %>% 
  filter(!is.na(unregion))

gpr_effects_job$group <- NA
gpr_effects_job$year <- as.numeric(gpr_effects_job$year)
gpr_effects_job$group[gpr_effects_job$year < 2020] <- "Pre-2020"
gpr_effects_job$group[gpr_effects_job$year == 2020] <- "2020"
gpr_effects_job$group[gpr_effects_job$year > 2020] <- "Post-2020"

gpr_effects_job_summary <- gpr_effects_job %>% 
  select(group, unregion, freq_first, freq_last) %>% 
  group_by(group, unregion) %>% 
  summarize(total_first = sum(freq_first, na.rm = T),
            total_last = sum(freq_last, na.rm = T)) %>% 
  filter(!is.na(unregion))

# pre 2020 ----
x_pre2020 <- chisq.test(gpr_effects_ed_summary[gpr_effects_ed_summary$group == "Pre-2020", c("total_first", "total_last")])
v_pre2020 <- v.chi.sq(x2 = x_pre2020$statistic, 
                      n = sum(x_pre2020$observed),
                      r = nrow(x_pre2020$observed),
                      c = ncol(x_pre2020$observed))

# 2020 ----
x_2020 <- chisq.test(gpr_effects_ed_summary[gpr_effects_ed_summary$group == "2020", c("total_first", "total_last")])
v_2020 <- v.chi.sq(x2 = x_2020$statistic, 
                      n = sum(x_2020$observed),
                      r = nrow(x_2020$observed),
                      c = ncol(x_2020$observed))

# post 2020 ----
x_post2020 <- chisq.test(gpr_effects_ed_summary[gpr_effects_ed_summary$group == "Post-2020", c("total_first", "total_last")])
v_post2020 <- v.chi.sq(x2 = x_post2020$statistic, 
                      n = sum(x_post2020$observed),
                      r = nrow(x_post2020$observed),
                      c = ncol(x_post2020$observed))
```

### 2022-06-06 04.manuscript.Rmd
updating manuscript pre-reg

**_Geopolitical Regions_**. We will present visualizations of the last listed education and job location, and we will discuss the areas of world in which authors generally come from, as well as the lowest representation of authors. To understand the change in representation diversity, we will summarize the total number of geopolitical regions for each paper. Using a linear model, we will examine if the number of regions present is predicted by the year of publication. Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope. Last, we will examine the differences in representation for corresponding author sets versus all other authors. For papers with 10 to 49 authors, we will use the three first authors and the last author to compare against random samples of other authors. For 50 to 99 authors, five first authors plus last will be used, and for all papers with more than 100 authors, we will use ten first authors and the last author. We will calculate the frequencies of each of the UN Sub-Regions for first authors. Then we will randomly sample all authors in subsets of the same size (i.e., 3+1, 5+1, 10+1), and average the frequencies of UN Sub-Regions across these random samples. We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six). For each year, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors. Since this data is categorical, we will use Cramer's V to represent the effect size. If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity. Any confidence interval that does include zero represents a difference in diversity. We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero.

@@

```{r}
edu_country_output <- tidy(edu_country_model)
job_country_output <- tidy(job_country_model)
```

Next, we will report the results of two linear regression models. The independent variable is year of publication, and the dependent variables include the summary of the total number of different geopolitical regions represented in each publication. 
- The slope for the education model was *b* = `r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r edu_country_output$df[2]`) = `r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(edu_country_output$p.value[2])`.

- The slope for the employment model was *b* = `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r job_country_output$df[2]`) = `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(job_country_output$p.value[2])`.

```{r eval = F}
gpr_effects_ed_summary <- 
  gpr_effects_ed %>% 
  group_by(year) %>% 
  summarize(v = mean(v, na.rm = T), 
            vlow = mean(low_v, na.rm = T), 
            vhigh = mean(high_v, na.rm = T))

gpr_effects_job_summary <- 
  gpr_effects_job %>% 
  group_by(year) %>% 
  summarize(v = mean(v, na.rm = T), 
            vlow = mean(low_v, na.rm = T), 
            vhigh = mean(high_v, na.rm = T))
```

Last, we will examine the effect sizes of the UN Sub-Regions represented for each year of analysis. We will present a visualization of the effect sizes.

- add a quick random demo of this simulating fake data
- create a picture of this idea

**All models will also include a measure of effect size.**
#### erin you need to do this #####

@@

Discuss the limitation of "who is using ORCID and Scholar" which can bias our results.

>>>>

**_Geopolitical Regions_**. We will present visualizations of the last listed education and job location, and we will discuss the areas of world in which authors generally come from, as well as the lowest representation of authors. To understand the change in representation diversity, we will summarize the total number of geopolitical regions for each paper. Using a linear model, we will examine if the number of regions present is predicted by the year of publication. Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope. Last, we will examine the differences in representation for corresponding author sets versus all other authors. For papers with 10 to 49 authors, we will use the three first authors and the last author to compare against random samples of other authors. For 50 to 99 authors, five first authors plus last will be used, and for all papers with more than 100 authors, we will use ten first authors and the last author. We will calculate the frequencies of each of the UN Sub-Regions for first authors. Then we will randomly sample all authors in subsets of the same size (i.e., 3+1, 5+1, 10+1), and average the frequencies of UN Sub-Regions across these random samples. We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six).

Given the expected small sample sizes of these contingency tables (i.e., the largest could be *n* = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time. The choice of these groupings is based on the number of articles avaliable within these time brackets. For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors. Since this data is categorical, we will use Cramer's V to represent the effect size. If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity. Any confidence interval that does include zero represents a difference in diversity. We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero using standardized residuals.

@@

```{r echo = F}
edu_country_output <- tidy(edu_country_model)
job_country_output <- tidy(job_country_model)
```

Next, we will report the results of two linear regression models. The independent variable is year of publication, and the dependent variables include the summary of the total number of different geopolitical regions represented in each publication. 
- The slope for the education model was *b* = `r format(round(edu_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(edu_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r edu_country_model$df.residual`) = `r format(round(edu_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(edu_country_output$p.value[2])`.

- The slope for the employment model was *b* = `r format(round(job_country_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(job_country_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r job_country_model$df.residual`) = `r format(round(job_country_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(job_country_output$p.value[2])`.

Last, we will examine the effect sizes of the UN Sub-Regions represented for each grouped year of analysis. Tables of the UN Sub-Regions will be presented in our supplemental documents.

- Pre-2020: `r v_pre2020$estimate` and `r x_pre2020$stdres` will be used to discuss pre-2020 manuscripts.

- 2020: `r v_2020$estimate` and `r x_2020$stdres` will be used to discuss 2020 manuscripts.

- Post-2020: `r v_post2020$estimate` and `r x_post2020$stdres` will be used to discuss post-2020 manuscripts.

@@

## Limitations

- Discuss the limitation of "who is using ORCID and Scholar" which can bias our results. 
- Other limitations will be included.

### 2022-06-06 04.manuscript.tex
updating manuscript pre-reg

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\title{Who does big team science?}
\author{Erin M. Buchanan\textsuperscript{1} \& Savannah C. Lewis\textsuperscript{2}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Who does big team science?},
  pdfauthor={Erin M. Buchanan1 \& Savannah C. Lewis2},
  pdflang={en-EN},
  pdfkeywords={big team, science, authorship, credit},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Big Team Science}
\keywords{big team, science, authorship, credit\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\textbf{\emph{Geopolitical Regions}}.
- overall map of where people get their education
- overall map of where people are working
- is this diversifying over time (more countries as years go up)
- then the weird analysis to answer about diversifying authors

@@

\textbf{\emph{Employment}}. Overall, individuals \textbf{at the time of publication} in big team science publications are Professor (28.8\%) and Assistant Professor (24.7\%), followed by smaller categories for Lecturer (16.4\%), Associate Professor ( 9.6\%), Post Doc (8.2\%), and Head (6.8\%). Here, we will talk about the figure below and how the trends occur across time. We will also comment on the number of jobs that would be considered ``non-academic.''

@@

\textbf{\emph{Education}}. Overall, individuals \textbf{at the time of publication} in big team science publications are Doctor (79.7\%), Masters (16.5\%), andBachelor (3.8\%). Here, we will talk about the figure below and how the trends occur across time.

@@

\textbf{\emph{Geopolitical Regions}}.
- overall map of where people get their education
- overall map of where people are working
- is this diversifying over time (more countries as years go up)
- then the weird analysis to answer about diversifying authors

@@

Discuss the limitation of ``who is using ORCID and Scholar'' which is likely biasing our results.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Who does big team science?},
  pdfauthor={Erin M. Buchanan1 \& Savannah C. Lewis2},
  pdflang={en-EN},
  pdfkeywords={big team, science, authorship, credit},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{big team, science, authorship, credit\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Who does big team science?}
\author{Erin M. Buchanan\textsuperscript{1} \& Savannah C. Lewis\textsuperscript{2}}
\date{}

\shorttitle{Big Team Science}

@@

\textbf{\emph{Geopolitical Regions}}. We will present visualizations of the last listed education and job location, and we will discuss the areas of world in which authors generally come from, as well as the lowest representation of authors. To understand the change in representation diversity, we will summarize the total number of geopolitical regions for each paper. Using a linear model, we will examine if the number of regions present is predicted by the year of publication. Increasing diversity would be represented by a positive slope, while decreasing diversity would be represented by a negative slope. Last, we will examine the differences in representation for corresponding author sets versus all other authors. For papers with 10 to 49 authors, we will use the three first authors and the last author to compare against random samples of other authors. For 50 to 99 authors, five first authors plus last will be used, and for all papers with more than 100 authors, we will use ten first authors and the last author. We will calculate the frequencies of each of the UN Sub-Regions for first authors. Then we will randomly sample all authors in subsets of the same size (i.e., 3+1, 5+1, 10+1), and average the frequencies of UN Sub-Regions across these random samples. We will randomly sample the same number of times as the size of the author list (i.e., a paper that has 54 authors will be randomly sampled 54 times with a sample size of six).

Given the expected small sample sizes of these contingency tables (i.e., the largest could be \emph{n} = 22 if all author information is available), we will group together titles based on time period using pre-2020, 2020, and post-2020 to show change over time. The choice of these groupings is based on the number of articles avaliable within these time brackets. For each grouping, we will calculate the effect size of the differences in frequencies comparing first authors to all other authors. Since this data is categorical, we will use Cramer's V to represent the effect size. If the effect size includes zero in it's confidence interval, this result will imply that first and all other authors represent the same pattern of UN Sub-Region diversity. Any confidence interval that does include zero represents a difference in diversity. We will report these values and discuss what regions of the world are represented when effect sizes indicate a different from zero using standardized residuals.

@@

\textbf{\emph{Employment}}. Overall, individuals \textbf{at the time of publication} in big team science publications are Professor (28.8\%) and Assistant Professor (24.7\%), followed by smaller categories for Lecturer (16.4\%), Associate Professor ( 9.6\%), Post Doc (8.2\%), and Head (6.8\%). Here, we will talk about the figure below and how the trends occur across time. We will also comment on the number of jobs that would be considered ``non-academic''.

@@

\textbf{\emph{Education}}. Overall, individuals \textbf{at the time of publication} in big team science publications are Doctor (79.7\%), Masters (16.5\%), and Bachelor (3.8\%). Here, we will talk about the figure below and how the trends occur across time.

@@

\textbf{\emph{Geopolitical Regions}}. We will first present two figures for education and employment geopolitical regions representation in scholars.

Education Graph

\includegraphics{04.manuscript_files/figure-latex/figure5-1.pdf}

Employment Graph

\includegraphics{04.manuscript_files/figure-latex/figure6-1.pdf}

Next, we will report the results of two linear regression models. The independent variable is year of publication, and the dependent variables include the summary of the total number of different geopolitical regions represented in each publication.
- The slope for the education model was \emph{b} = 0.06, \emph{SE} = 0.09, \emph{t}(68) = 0.63, \emph{p} = .531.

\begin{itemize}
\tightlist
\item
  The slope for the employment model was \emph{b} = 0.01, \emph{SE} = 0.09, \emph{t}(68) = 0.12, \emph{p} = .903.
\end{itemize}

Last, we will examine the effect sizes of the UN Sub-Regions represented for each grouped year of analysis. Tables of the UN Sub-Regions will be presented in our supplemental documents.

\begin{itemize}
\item
  Pre-2020: \(V\) = .36, 95\% CI {[}.54, .78{]} and 0.13, 0.44, 0.94, -0.57, -0.84, -0.57, -0.13, -0.44, -0.94, 0.57, 0.84, and 0.57 will be used to discuss pre-2020 manuscripts.
\item
  2020: \(V\) = .64, 95\% CI {[}.48, 1.19{]} and -0.66, 2.31, -1.02, -0.84, 0.66, -2.31, 1.02, and 0.84 will be used to discuss 2020 manuscripts.
\item
  Post-2020: \(V\) = .55, 95\% CI {[}.65, 1.28{]} and 1.45, -0.68, -0.68, -0.68, -1.45, 0.68, 0.68, and 0.68 will be used to discuss post-2020 manuscripts.
\end{itemize}

@@

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

\begin{itemize}
\tightlist
\item
  Discuss the limitation of ``who is using ORCID and Scholar'' which can bias our results.
\item
  Other limitations will be included.
\end{itemize}
